%section Introduction
\section{Introduction}
\begin{comment}
What I could also mention:
\cite{2018_Brandao} mentions that they concluded in their study, that there is a growing importance of certain areas in the blockchain research. One of these areas is smart cities and business which impacts our team, smart industry ! The term smart places includes the term smart industry because the industry is nothing but another place to use IoT/ Blockchain smart factory / smart manufacturing
\end{comment}
Starting to work in the context of industrial maintenance, I focused my research on current technologies in the field.\\
I did not have to look far to come to the conclusion, that the fourth industrial revolution is currently ongoing. In Germany the term ‘Industry 4.0’ emerged as a label for it and was widely accepted. There are certain technologies or more methodologies that play an important role: Machine Learning, Big Data, Data Analytics, Internet of Things (IoT), Blockchain and many more. \\
In the smart factory, mainly IoT technologies are implemented at this instant, to connect machines to other machines and make them work more autonomously. These IoT devices are usually connected by a centralized server in the cloud and focus on the server-client model. One of the main issues here is to find something that decentralizes the control of these IoT devices. Here the Blockchain (BC) is a technology that recently got a lot of attention. It was first used as the underlying technology to the cryptocurrency Bitcoin. Connecting these two technologies would therefore be an opportunity to provide a decentralized system. \\
Since there are not many defined standards describing Blockchain technology, it was quite hard to start the research. Digging deeper, I figured out, that there is a high need for use cases (empirical studies), so that for different areas, the advantages and drawbacks of the solutions can be tested. Reading the review papers on Blockchain use cases, I realized that neither of them were able to answer my question, neither to provide me with a good overview. I started to design my own schema to analyze the use cases and then tested it on some use cases.\\
The paper is structured as follows: in Chapter \ref{sec:Background}, a Background on the basics of the Blockchain technology and the state of the art in blockchain reviews are presented, in Chapter \ref{sec:Approach}, my approach for information selection and the papers I selected to be analyzed, in Chapter 3, my approach on defining the criteria used to differentiate the selected paper, in chapter 4, the papers are discussed according to the criteria that were presented in chapter 3. In the 5th chapter, the results of chapter 4 are discussed, chapter 5 is the solution and presents further research opportunities.
